Individual and Differential Harm in Redistricting

### 2022-05-04 paper/paper.Rmd
AL and NJ figures

Suppose now that plan (a) is enacted into law.
Who does this decision harm, if anyone?
We offer that a voter is harmed if they are not represented by their party of choice, but have a counterfactual where they would be represented by their party of choice.
Using plan (b) as a counterfactual, we can see that rural Republicans in the eastern half of Mininois are harmed by plan (a), since under plan (b) they would be represented by a Republican.
Republicans in the city and in the southwest are unharmed, as are all Democratic voters,, since they are represented by the same party under both plans.
Figure \ref{fig:harm-mininois}, Panel C illustrates this by plotting the number of voters harmed in each precinct.

@@

```{r nj-maps, fig.width=6.5, fig.height=3}
#| fig.cap: |
#|      Baseline vote patterns, two hypothetical gerrymanders, 
#|      and one randomly sampled plan.
#|      Census-designated places are shaded in gray and county lines in white.
include_graphics("figures/nj_maps.pdf")
```

@@

@@

```{r boston-map, fig.width=6.75, fig.height=3.375}
#| fig.cap: |
#|      Racial composition of the city of Boston (left), 
#|      and 2010 city coucil districts (right).
#|      Neighborhood boundaries are overlaid in black on the left map and in white on the right map.
include_graphics("figures/boston_map.pdf")
```

>>>>

Suppose now that plan (a) is enacted into law.
Who does this decision harm, if anyone?
We offer that a voter is harmed if they are not represented by their chosen party, but would have been so counterfactually.
Using plan (b) as a counterfactual, we can see that rural Republicans in the eastern half of Mininois are harmed by plan (a), since under plan (b) they would be represented by a Republican.
Republicans in the city and in the southwest are unharmed, as are all Democratic voters,, since they are represented by the same party under both plans.
Figure \ref{fig:harm-mininois}, Panel C illustrates this by plotting the number of voters harmed in each precinct.

@@

```{r nj-maps, fig.width=6.5}
#| fig.cap: |
#|      Baseline vote patterns (a), two hypothetical gerrymanders (b) and (c), 
#|      and one randomly sampled plan (d).
#|      Census-designated places are shaded in gray and county lines in white.
include_graphics("figures/nj_maps.pdf")
```

@@

# Application to Voting Rights Litigation in Alabama {#sec:alabama}

```{r al-maps, fig.width=6.5}
#| fig.cap: |
#|      Baseline vote patterns (a), 
#|      fraction of the voting-age population which is Black (b),
#|      and fraction of voters in each precinct which are harmed by the 2020
#|      enacted congressional districts versus the set of four remedial plans (c).
#|      2020 enacted district boundaries are overlaid 
#|      in black on the left map and in white on the right maps.
include_graphics("figures/al_maps.pdf")
```

Differential racial harm: 0.23708

Differential partisan harm: 0.20939

Total harm: 0.089009

Average total harmed: 162390

Average total harmed by group:

| Average total harmed | Democratic | Republican |
|----------------------|------------|------------|
| **White**            | 28,476     | 7,867      |
| **Black**            | 125,635    | 147        |
| **Other**            | 257        | 7.4        |

: This table is just a placeholder to store the numbers.

[More text after the table.]

@@

```{r boston-map, fig.width=6.75, fig.height=3.375}
#| fig.cap: |
#|      Racial composition of the city of Boston (left), 
#|      and 2010 city coucil districts (right).
#|      Neighborhood boundaries are overlaid in black on the 
#|      left map and in white on the right map.
include_graphics("figures/boston_map.pdf")
```
